%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.3, 10 May 2020) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}
%% AltaCV uses the fontawesome5 and academicons fonts
%% and packages.
%% See http://texdoc.net/pkg/fontawesome5 and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Change the colours if you want to
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{450808}
\definecolor{PastelRed}{HTML}{8F0D0D}
\definecolor{GoldenEarth}{HTML}{E7D192}
\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}


% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Lars Quentin}
\tagline{Computer Science Student, Programmer}

\personalinfo{%
  \email{lars@lquenti.de}
  \location{G\"ottingen, Deutschland}
  \homepage{lquenti.de}
  \github{lquenti}
  \gitlabgwdg{lars.quentin}
  \linkedin{lars-quentin-68375217a}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
  % \orcid{0000-0000-0000-0000}
  %% You can add your own arbtrary detail with
  %% \printinfo{symbol}{detail}[optional hyperlink prefix]
  % \printinfo{\faPaw}{Hey ho!}[https://example.com/]
  %% Or you can declare your own field with
  %% \NewInfoFiled{fieldname}{symbol}[optional hyperlink prefix] and use it:
  % \NewInfoField{gitlab}{\faGitlab}[https://gitlab.com/]
  % \gitlab{your_id}
}

\makecvheader
%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.6}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}
\cvsection{Employment History}

\cvevent{Student Researcher}{Gesellschaft f\"ur wissenschaftliche Datenverarbeitung G\"ottingen}{2021 October -- now}{G\"ottingen}
\cvtag{High Performance Computing}
\cvtag{Storage}
\cvtag{Data Science}
\medskip
\begin{itemize}
\item Creating a Black-Box method for classifying I/O-Requests in linux-based systems.
\end{itemize}

\divider
\cvevent{IT-Support and Web development}{Max-Planck-Institut f\"ur biophysikalische Chemie}{2017 September -- 2021 Sept.}{G\"ottingen}
\cvtag{Python}
\cvtag{Django}
\cvtag{Linux}
\cvtag{Client Support}
\medskip
\begin{itemize}
\item First- and Second-Level Support
\item Concept and Implementtion of a Django-based web frontend for long term data archivation
\end{itemize}

\divider

\cvevent{Full-Stack PHP-Developer}{Universit\"at des Dritten Lebensalters G\"ottingen e.V.}{2020 February -- 2021 January}{G\"ottingen}
\cvtag{PHP}
\cvtag{ES6+}
\cvtag{Bootstrap}
\cvtag{docker}
\medskip
\begin{itemize}
\item Development and Maintenance of internal PHP-Framework
\end{itemize}

\divider

\cvevent{Tutor Programming Course}{Georg-August-Universit\"at G\"ottingen}{2019 April -- 2019 October}{G\"ottingen}
\cvtag{Java}
\cvtag{Git}
\cvtag{Swing}
\cvtag{Graphentheorie}
\medskip
\begin{itemize}
\item Supervision of bachelor students
\item Task: Creating a turn based video game in Java
\item Average Grade my groups recieved: 1.4
\end{itemize}

\divider

\cvevent{Internship}{Max-Planck-Institut für Dynamik und Selbstorganisation}{2015 September -- 2016 May}{G\"ottingen}
\cvtag{Bash}
\cvtag{Linux}
\cvtag{Python}
\medskip
\begin{itemize}
\item Installation and Configuration of several Linux distributions.
\item First programming experience in bash as well as Python2
\item First experience with Linux Server administrations, especially old school Webstacks and LXC
\end{itemize}

\cvsection{Selected Open Source Projects}

\cvevent{\href{https://github.com/lquenti/blackheap}{blackheap (actively developed)}}{\href{https://github.com/lquenti/blackheap}{https://github.com/lquenti/blackheap}}{}{}
\cvtag{Rust}
\cvtag{C}
\cvtag{Benchmarking}
\cvtag{Statistical Modelling}
\medskip
\begin{itemize}
\item Creates linear models for characterizing I/O accesses.
\item Blackbox approach, doesn't require any knowledge about the storage system.
\item Benchmarker written in C and Rust.
\item Can be integrated with iofs.
\end{itemize}

\divider

\cvevent{\href{https://github.com/gwdg/iofs}{iofs (Maintainer)}}{\href{https://github.com/gwdg/iofs}{https://github.com/gwdg/iofs}}{}{}
\cvtag{C}
\cvtag{FUSE}
\cvtag{Monitoring}
\cvtag{InfluxDB}
\medskip
\begin{itemize}
\item FUSE-based filesystem for logging I/O accesses.
\item Remounts local filesystem for metric aggregation.
\item Supports metric streaming to Elasticsearch and InfluxDB (v1).
\end{itemize}

\divider

\cvevent{\href{https://github.com/lquenti/walky/}{walky}}{\href{https://github.com/lquenti/walky/}{https://github.com/lquenti/walky/}}{}{}
\cvtag{Rust}
\cvtag{MPI}
\cvtag{Algorithms}
\cvtag{HPC}
\medskip
\begin{itemize}
\item Rust-based Travelling Salesman Problem Solver.
\item Exact solver and multiple approximation algorithms.
\item Multi node MPI support using rsmpi.
\end{itemize}

\divider

\cvevent{\href{https://github.com/lquenti/ankiding}{ankiding}}{\href{https://github.com/lquenti/ankiding}{https://github.com/lquenti/ankiding}}{}{}
\cvtag{Rust}
\cvtag{Markdown}
\cvtag{Anki}
\cvtag{CI/CD pipeline}
\cvtag{\LaTeX{}}
\medskip
\begin{itemize}
\item Defines a GFM/GLFM syntax extension for flashcards.
\item Exports markdown files with flashcards to Anki decks.
\item Can be used automatically in CI-Systems.
\item Supports \LaTeX{} formulas on Mobile.
\end{itemize}

\divider

\cvevent{\href{https://gitlab.gwdg.de/numerikgang/curvepy}{curvepy}}{\href{https://numerikgang.pages.gwdg.de/}{Numerikgang}}{}{}
\cvtag{Python}
\cvtag{Numerics}
\cvtag{Computational Geometry}
\medskip
\begin{itemize}
\item High Performance Pythonlibrary for computational geometry
\item Focus on Bezier Curves and Voronoi Regions via Delaunay Triangulations
\item High Test- and Docstring Coverage
\end{itemize}

\divider

\cvevent{Programming Course for Law Students}{eLegal e.V., \href{https://www.elegal.technology/}{https://www.elegal.technology/}}{}{}
\cvtag{Teaching}
\cvtag{Java}
\cvtag{Apache POI}
\medskip
\begin{itemize}
\item An Introduction to Legal-Tech
\item Created for this course: \href{https://github.com/elegal-ev/Keres}{Keres, a graphical Word template engine}
\item Postponed due to Corona
\end{itemize}


% use ONLY \newpage if you want to force a page break for
% ONLY the current column
\newpage

%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

\cvsection{Education}
\cvevent{Applied Computer Science B.Sc}{Georg-August-Universit\"at G\"ottingen}{2023 Janurary -- now}{}
Current Average Grade: 1.0\\
\divider
\cvevent{Applied Computer Science B.Sc}{Georg-August-Universit\"at G\"ottingen}{2017 October -- 2022 December}{}
Average Grade: 2.0\\
\divider
\cvevent{Fachhochschulreife Informatik}{BBS 2 G\"ottingen}{2015 -- 2017}{}
Average Grade: 2.2\\

\medskip

\cvsection{Technologien}

\cvskill{Python}{5}
\divider
\cvskill{Linux}{5}
\divider
\cvskill{Rust}{4}
\divider
\cvskill{Git}{4}
\divider
\cvskill{C}{4}
\divider
\cvskill{C++}{3}

\divider

\cvsection{Interests}
\cvtag{Performance Engineering}\cvtag{HPC}\\
\cvtag{Scalable Architecture}\cvtag{Cloud Computing}\\
\cvtag{System development}\\
\cvtag{Algorithms \& Data Structures}

\divider

% move to next page
\vspace*{3cm}

\cvsection{Volunteering Work}

\cvevent{IT-Administrator and Student Rental Service}{Studentendorf G\"ottingen}{2022 April -- now}{G\"ottingen}
\cvtag{Docker}
\cvtag{VMWare}
\cvtag{Wordpress}\\
\cvtag{Mailcow}
\medskip
\begin{itemize}
\item Maintenance of dorm infrastructure
\item VMWare Hypervisor administration
\item Dockerization of Website and Mailserver (Infrastructure as Code)
\item Building rsync-based rolling backup solution on tape
\end{itemize}

\divider 

\cvevent{Teacher/Developer}{eLegal e.V., \href{https://www.elegal.technology/}{https://www.elegal.technology/}}{2019 Janurary -- 2020 Janurary}{}
\cvtag{Teaching}
\cvtag{Java}\\
\medskip
Designing a Java programming couse for law students based on a custom docx-based cease and desist generator. Indefinitely postponed due to COVID-19.

\end{paracol}


\end{document}
